Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-05-16 tex/ms.tex
working on results section

% ---- Hogg (aastex) mode ----
%\documentclass[12pt, letterpaper, preprint]{aastex}
% ----

% ---- Charlie (emulateapj) mode ----
 \documentclass[iop,numberedappendix]{emulateapj}
 \usepackage{apjfonts}
% ----

@@

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z [, \beta]) \, e^ {-k_\lambda\tau_V}  + \\
& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2}}
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_n \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
and redshift $z$,
and amplitudes of the $N_l$ nebular and interstellar emission lines
$a_i$.

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, using the full YY-band photometry.

NEEDS MASSIVE REWORDING.
In Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,\alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and individual components of the model
constructed from each draw.   In Figure \ref{fig:calibrated_residuals}
we show the residuals between the data and the draws from the
posterior, for the spectra and the photometry.

In Figure \ref{fig:calibrated_triangle} we show the marginalized and
joint PDFs for the parameters.

Apparently we get really nice redshift/velocity constraints for free.

>>>>

% ---- Hogg (aastex) mode ----
\documentclass[12pt, letterpaper, preprint]{aastex}
% ----

% ---- Charlie (emulateapj) mode ----
% \documentclass[iop,numberedappendix]{emulateapj}
% \usepackage{apjfonts}
% ----

@@

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V}  + \\
& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2}}
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_n \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
and redshift $z$,
and amplitudes of the $N_l$ nebular and interstellar emission lines
$a_i$.

@@

We first infer the parameters of interest $\theta$ for a calibrated
spectrum of one of the clusters, using the full YY-band photometry. In
Figure \ref{fig:calibrated_spectrum} we show the spectrum resulting
from draws of the parameters $[\theta,\alpha]$ from the posterior
distribution.  This figure also shows the calibrated spectrum on which
the priors were conditioned, and several of the individual components
of the model constructed from each draw.  In Figure
\ref{fig:calibrated_residuals} we show the residuals between the data
and the draws from the posterior, for both the spectra and the
photometry. In Figure \ref{fig:calibrated_triangle} we show the
marginalized and joint PDFs for the parameters.

Discuss degeneracies, etc.  Apparently we get really nice
redshift/velocity constraints for free.

Next, we infer the parameters of the spectrum of the same cluster
\emph{without} spectrophotometric calibration.
